
Data from `r year` have 
`r length(d[[1]])` observations from 
`r length(d)` variables: *`r names(d)`*.

#### Factor variables

```{r }
fv <-  # Factor variables
  c("Group", "Week", "Date", "Species", "Use",
    "Treatment", "Too_dry", "Mortality")

txt <- ""
for (i in fv) {
  l <- levels(as.factor(d[[i]]))
  na <- sum(is.na(d[[i]]))
  txt <- paste(txt, "\n\n",
    paste0("The **_", i, "_** variable has ", 
      na, " missing values and ", 
      length(l), " levels: ", 
      paste(l, collapse = ", "), "."))
}

```

There are 
`r length(fv)` factor variables in 
`r year` data, including *Date* (that is not exactly a factor): 
*`r fv`*.

`r txt`

#### Numerical variables

```{r }
tf <- sapply(names(d), function(x) is.numeric(d[[x]]))
nv <- names(d)[tf]

txt <- ""
for (i in nv) {
  na <- sum(is.na(d[[i]]))
  m <- min(d[[i]], na.rm = TRUE)
  M <- max(d[[i]], na.rm = TRUE)
  txt <- paste(txt, "\n\n",
    paste0("The **_", i, "_** variable has ", 
      na, " missing values and range from ", 
      m, " to ", M, "."))
}
```

There are `r length(nv)` numerical variables in 
`r year` data: *`r nv`*.

`r txt`

### Sample size

In the next table, check that all PlantID were measured every week. And only once:

```{r}
table(d$PlantId, d$Week)

```


### Comments

```{r}
tf <- is.na(d$Comments)
if (all(tf)) 
  txt <- paste0("There are NO comments in ", 
    year, " data.")
if (!all(tf)) 
  txt <- paste0("There are ", sum(!tf), " comments in ", 
    year, " data: ", 
    paste(levels(as.factor(d$Comments)), 
      collapse = ", "), ".")


```

`r txt`
