---
# author:
# - affiliation: Instituto Agroforestal Mediterráneo. Departamento de Ecosistemas Agroforestales.
#   email: algarsal@upv.es
#   name: Alfonso Garmendia
title: Drip & drown
subtitle: Navigating the plant stress
title-block-banner: true
date: last-modified
date-format: iso
lang: en-EN
language: 
  title-block-published: "Last modified"
code-fold: true
toc: true
toc-location: body
toc-depth: 6
toc-title: Contents
format:
  html:
    embed-resources: true
    self-contained-math: true
editor: 
  markdown: 
    wrap: 72
---

```{r include=FALSE}
library(knitr)
```

## Import data

```{r download, eval=!dir.exists("data")}
# dir()
# source("00a_data-download.R")
# source("00b_data-bind.R")

```

If there are changes in the original Google-Drive data: 

1. **_00a_data-download.R_** script should be run to download data. 2. **_00b_data-bind.R_** script should be run bind data in only one table.

```{r}
# dir("data", full.names = TRUE)
load("data/bound-data.Rdata")
```

Bound data are loaded from the file **_data/bound-data.Rdata_**: `r ls(pattern = "b")`.

- **datab** are the data from the plants, all years. 
- **datesb** have the important dates. 
- **legendb** have the legend to describe variables. 

## Legend

Final legend for unified data is in @tbl-legend.

```{r tbl-legend}
#| tbl-cap: Legend for unified data. 
kable(legendb)
```


### Check variables names

```{r}
vn.data <- names(datab)
vn.lege <- legendb$Variable
```

```{r legend-names}
tf <- vn.data %in% vn.lege

if (all(tf)) {
  txt <- paste("OK, all variables names in data are included in the legend.")
}
if (!all(tf)) {
  txt <- paste0("NOT ALL variables names in the data are included in the legend table: ",
    paste(vn.data[!tf], collapse = ", "), ".")
}

tf <- vn.lege %in% vn.data

if (all(tf)) {
  txt2 <- paste("OK, all variables names in legend are included in the data.")
}
if (!all(tf)) {
  txt2 <- paste0("NOT ALL variables names in the legend are included in the data table: **_",
    paste(vn.lege[!tf], collapse = ", "), "_**.")
}

```

`r txt`

`r txt2`


## Dates 

Important dates from data of each year are in @tbl-dates

```{r tbl-dates}
#| tbl-cap: Important dates from data. 
kable(datesb)
```

## Data

Data table is in @tbl-data.

```{r tbl-data}
#| tbl-cap: First 10 observations from data table. 
#| column: screen-inset
kable(datab[1:10, ])
```

### Check data

```{r}
d <- datab
year <- "bound table"
# dir("rmd")
```

{{< include rmd/_factor-numeric.qmd >}}

# {{< pagebreak >}}

{{< include rmd/_reproducibility.qmd >}}


```{r}
knit_exit()
```
